---
title: "stratification table"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(tidyverse)
library(ggthemes)
library(gridExtra)
library(janitor)
library(crayon)
library(ggplot2)
library(viridisLite)
library(generalizeRdata)
library(generalizeR)
library(cluster)
library(ClusterR)
library(knitr)
library(kableExtra)

source("/Users/beatricechao/Documents/STEPP/generalizeR/R/assess_wrap.R")


```

### Summary of stratify() function

Let’s say the user saves the stratification object as stratify_object 

```{r cars, results = FALSE, fig.show='hide', warning = FALSE}

selection_vars <- c("pct_female", "pct_black_or_african_american", "pct_free_and_reduced_lunch")

inference_pop <- cc %>% 
  filter(charter == 1) %>%
  filter(g_10_offered == "Yes") %>% 
  select(ncessch, all_of(selection_vars))

stratify_results <- stratify(inference_pop, guided=F, n_strata = 4, variables = selection_vars,idnum = "ncessch")

```

We want to make sure that they are able to call up their object again to see the summary of their output again. Currently, when you print "stratify_results", you get all the information stored as lists within the stratify_results object, which is obviously not ideal (and too long to print even here).

Compare this to assess function, which gives you a summary of the choices you made in the function

```{r cars3, warning = FALSE}
sample <- tibble(ncessch = c(stratify_results$recruitment_lists[[1]]$ncessch[1:20],
                             stratify_results$recruitment_lists[[2]]$ncessch[1:4],
                             stratify_results$recruitment_lists[[3]]$ncessch[1:6],
                             stratify_results$recruitment_lists[[4]]$ncessch[1:11]))

gen_results <- assess_wrap(sample,inference_pop,join_var = "ncessch")

gen_results

```

When you do summary(gen_results) [as you would do summary(lm), when trying to fit a linear model], it gives the following 


```{r cars4, warning = FALSE}

summary(gen_results)

```


